---
title: "PEPATAC BiocProject"
author: c("Michal Stolarczyk", "Jason Smith")
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PEPATAC BiocProject}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

Before you start see the [Getting started with `BiocProject` vignette](http://code.databio.org/BiocProject/articles/vignette1getStarted.html) for the basic `BiocProject` information and installation instructions and [`PEPATAC` website](http://pepatac.databio.org) for information regarding this ATAC-seq pipeline.

`BiocProject` provides a slick way of reading in the outputs of the pipeline listed in the `outputs` section of its [pipeline interface](http://code.databio.org/looper/pipeline-interface/). 

__With a single line of code you can read all the indicated results and your project metadata.__

# Read the results of `PEPATAC` run

The function shown below reads in the `BED` files from the `output` section specified in the [`PEPATAC` pipeline interface](https://github.com/databio/pepatac/blob/master/pipeline_interface.yaml).

The way the output files are read is defined in a [function](https://github.com/databio/pepatac/blob/master/BiocProject/readPepatacPeakBeds.R) supplied by the `PEPATAC` developers. The function listed in `bioconductor` section of `PEPATAC` pipeline interface file is identified by `BiocProject` function, sourced and automatically executed on samples matching the protocols bound to the pipeline specified as an argument in [`outputsByPipeline`](http://code.databio.org/BiocProject/reference/outputsByPipeline.html) function.

## Get the project config

```{r echo=T, message=FALSE}
library(BiocProject)
ProjectConfig = "gold_config.yaml"
```

## Run the `BiocProject` function

```{r}
bp = BiocProject(ProjectConfig)
```

As you can see in the message above, the `readPepatacPeakBeds` function was sourced from the file indicated in the `PEPATAC` pipeline interface.

## Browse the results

The read data is conveninetly stored in a `List` object with ([`pepr::Project`](http://code.databio.org/pepr/reference/Project-class.html) object in its metadata slot:

```{r}
bp
```